### 2021-04-26 input/introduction.tex
meow

\begin{asparadesc} %% to remove left-margin :p
\item [$\bullet$] We highlight the properties that guarantee
  decentralized consistent partitioning in dynamic infrastructures. We
  demonstrate that concurrent creation and removal of partitions may
  impair the propagation of control information crucial for consistent
  partitioning. Yet, \processes are able to purge stale information
  forever using only neighbor-to-neighbor communication, hence leaving
  room for up-to-date information propagation, and eventually
  consistent partitioning.
\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its
  partitioning, \ie \underline{s}copes, to creations and deletions of
  partitions in the system. \NAME relies on a communication primitive
  \underline{s}coped-broad\underline{cast} as \TODO{a communication
    primitive that allows epidemic dissemination of messages as long
    as receiving \processes verify an application-dependant
    predicate.}

\end{asparadesc}

@@

\noindent In addition, \NAME guarantees that despite concurrent
operations, every \process eventually knows one, and only one, source:
its closest. \NAME being reactive, when the system becomes quiescent,
\processes do not require further communications.
%% This primitive is used to guarantee that eventually, every node knows
%% its best partition, hence its closest replica, despite concurrent
%% events and receipt orders. Overall, \NAME is a wait-free reactive protocol for
%% dynamic logical partitioning.  Its overhead actually depends on
%% its operations and current partitions in the system. When the system
%% becomes quiescent, nodes eventually converge to their respective
%% partition and do not require further communication afterward.
% \TODO{talk about the proof}

\noindent Simulations empirically support our complexity analysis and
the scalability of \NAME in large scale networks comprising 10k
\processes. Our experiments also highlight the relevance of \NAME in
autonomous systems. \NAME would allow to lock down the traffic
generated by content indexing, even in contexts where \emph{physical}
partitioning may occur.

\noindent In that regard, \NAME can constitute the building block of
new geo-distributed services.

>>>>

\begin{asparadesc} %% to remove left-margin :p
\item [$\bullet$] We highlight the properties that guarantee
  decentralized consistent partitioning in dynamic infrastructures. We
  demonstrate that concurrent creation and removal of partitions may
  impair the propagation of control information crucial for consistent
  partitioning. Yet, \processes are able to purge stale information
  forever using only neighbor-to-neighbor communication, hence leaving
  room for up-to-date information propagation, and eventually
  consistent partitioning.
\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions in the system. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.
\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME in large scale networks comprising 10k \processes. Our
  experiments also highlight the relevance of \NAME in autonomous
  systems. \NAME would allow to lock down the traffic generated by
  content indexing, even in contexts where \emph{physical}
  partitioning may occur.
\end{asparadesc}

@@

% % %% \noindent In addition, \NAME guarantees that despite concurrent
% % %% operations, every \process eventually knows one, and only one, source:
% % %% its closest.
% % %% \NAME being reactive, when the system becomes quiescent, \processes do
% % %% not require further communications.

%% This primitive is used to guarantee that eventually, every node knows
%% its best partition, hence its closest replica, despite concurrent
%% events and receipt orders. Overall, \NAME is a wait-free reactive protocol for
%% dynamic logical partitioning.  Its overhead actually depends on
%% its operations and current partitions in the system. When the system
%% becomes quiescent, nodes eventually converge to their respective
%% partition and do not require further communication afterward.
% \TODO{talk about the proof}

\noindent \NAME can constitute a new building block for
geo-distributed services.
